\section{References}\label{references}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1289}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.8711}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
ABC01
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
ABC News Productions Nightline, ``The Deep Dive,'' Video \#N990713-51,
dated July 13, 1999, Copyrighted 2001.
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
ABE03 & \emph{Criteria for Accrediting Engineering Programs}, ABET
Engineering Accreditation Commission, 2003. \\
Abl91 & R. Abler, ``Good Product Designs Start with Good
Specifications,'' \emph{Medical Device Diagnostic Industry}, pp.
156-157, June 1991. \\
Ada01 & J.L. Adams, \ul{Conceptual Blockbusting}, 4\textsuperscript{th}
Edition, Perseus Publishing, 2001. \\
Alb06 & L. Al-Busaidi, M. Bellavia, and E. Roseborough,
``iPod\textsuperscript{TM} Hands Free Device,'' \emph{Penn State Behrend
Electrical and Computer Engineering Senior Design Report}, 2006. \\
Alt99 & G. Altshuller, \ul{The Innovation Algorithm: TRIZ, Systematic
Innovation, and Technical Creativity}, Technical Innovation Center,
1999. \\
And06 & N. Andre, J. Kolb, and J. Thaler, ``Portable Aerial Surveillance
System,'' \emph{Penn State Behrend Electrical and Computer Engineering
Senior Design Report}, 2006. \\
Ang00 & R.B. Angus, N.R. Gunderson, and T.P. Cullinane, \ul{Planning,
Performing and Controlling Projects: Principles and Applications},
2\textsuperscript{nd} Edition, Prentice Hall, 2000. \\
App01 & D. Apple and K. Krumsieg, \ul{Pacific Crest Teaching Institute
Handbook}, 2001. \\
Bai81 & J.E. Baird Jr., ``How to Overcome Errors in Public
Speaking\emph{,'' IEEE Transactions on Professional Communication,} vol.
PC-24, no. 2, pp. 94--98, 1981. \\
Bee03 & D.F. Beer, editor, \ul{Writing and Speaking in the Technology
Professions: A Practical Guide}, Wiley-IEEE Press, 2003. \\
Bel94 & L. Bellamy, D. Evans, D. Linder, B. McNeill, and G. Raupp,
\emph{Team Training Workbook}, Arizona State University, 1994. Available
at

\textless{}\url{http://www.eas.asu.edu/\%7Easufc/teaminginfo/teamwkbk.pdf}\textgreater. \\
Ben01 & S. Bennett and J. Skelton, \ul{Schaum's Outline of UML}, McGraw
Hill, 2001. \\
Bur03 & E.M. Burke and B.M. Coyner, \ul{Java Extreme Programming
Cookbook}, O'Reilly, 2003. \\
Cag02 & J. Cagan and C.M. Vogel, \ul{Creating Breakthrough Products:
Innovation from Product Planning to Program Approval}, Financial
Times/Prentice Hall, 2002. \\
Car89 & G. Carle, ``Handling a Hostile Audience--With Your Eyes,''
\emph{IEEE Transactions on Professional Communication}, vol. 32, no. 1,
pp. 29--31, 1989. \\
Cha71 & N. Chapin, \ul{Flowcharts}, Auerbach, 1971. \\
Cha02 & K. Chakraborty and P. Mazumder, \ul{Fault-Tolerance and
Reliability Techniques for High-Density Random-Access Memories},
Prentice Hall PTR, 2002. \\
Cha02b & T. Chambers, ``A Piercian Approach to Professional Ethics
Instruction,'' \emph{IEEE Transactions on Professional Communication},
vol. 45, no. 1, pp. 45--49, March, 2002. \\
Cro00 & N. Cross, \ul{Engineering Design Methods: Strategies for Product
Design}, 3\textsuperscript{rd} Edition, John Wiley \& Sons, 2000. \\
Deb67 & E. DeBono, \ul{New Think: The Use of Lateral Thinking in the
Generation of New Ideas}, New York, Basic Books, 1967. \\
Deb70 & E. DeBono, \ul{Lateral Thinking: Creativity Step by Step},
Harper and Row, 1970. \\
Dec84 & B. Decker, ``A Good Speech is Worth a Thousand Words,''
\emph{IEEE Transactions on Professional Communication}, vol. PC-27, no.
1, pp. 32--34, March, 1984. \\
Deg81 & R.T. DeGeorge, ``Ethical Responsibilities of Engineers in Large
Organizations: The Pinto Case,'' \emph{Business and Professional Ethics
Journal}, vol. 1, no. 1, pp. 1--14, 1981. \\
Del71 & A.L. Delbecq and A. H. VandeVen, ``A Group Process Model for
Problem Identification and Program Planning,'' \emph{Journal of Applied
Behavioral Science} \emph{VII}, pp. 466-491, July/August, 1971. \\
Die00 & G.E. Dieter, \ul{Engineering Design}, 3\textsuperscript{rd}
Edition, McGraw-Hill, 2000. \\
Dom01 & P.G. Dominick \emph{et al.}, \ul{Tools and Tactics of Design},
John Wiley \& Sons, 2001. \\
Dym94 & C. Dym, \ul{Engineering Design: A Synthesis of Views}, Cambridge
University Press, 1994. \\
Elm94 & R. Elmasri and S.B. Navathe, \ul{Fundamentals of Database
Systems}, Cummings, 1994. \\
Ern97 & R. Ernst, \ul{Embedded System Architectures in Hardware/Software
Co-Design: Principles and Practice}, Kluwer Academic Publishers,
1997. \\
Ese03 & T. Esek, J. Hunt, and N. Lewis, ``Intel Pro 1000XF Server
Testing,'' \emph{Penn State Behrend Electrical and Computer Engineering
Senior Design Report}, 2003. \\
Far02 & J. Farrell, \ul{Programming Logic and Design,}
2\textsuperscript{nd} Edition, Thomson Learning, 2002. \\
Fis04 & K.J. Fisher, M.J. Lobaugh, and D.H. Parente, ``An Assessment of
Desired Business Knowledge Attributes for Engineering and Technology
Graduates,'' Submitted to the \emph{Journal of Engineering Technology,}
July 2004. \\
Gar91 & J.C. Garland, ``Advice to Beginning Physics Speakers,''
\emph{Physics Today}, pp. 42--45, July, 1991. \\
Gob99 & A. Gobold, ``What has Ethics to do with me? I am an Engineer,''
\emph{Engineering Management Journal}, vol. 9, no. 2, pp. 81--86,
1999. \\
Gra85 & J. Gray. ``Why do Computers Stop and What Can be Done About
it?,'' \emph{Tandem Technical Report 85.7}, 46 pages, 1985. \\
Gra02 & C.F. Gray and E.W. Larson, \ul{Project Management},
2\textsuperscript{nd} Edition\emph{,} McGraw-Hill, 2002. \\
Gri93 & A. Griffin and J.R. Hauser, ``The Voice of the Customer,''
\emph{Marketing Science}, vol. 12, no. 1, pp. 1--27, 1993. \\
Hau88 & J.R. Hauser and D. Clausing, ``The House of Quality,''
\emph{Harvard Business Review}, pp. 63--73, May/June, 1988. \\
Hna03 & E.R. Hnatek, \ul{Practical Reliability of Electronic Equipment
and Products}, Marcel Dekker, 2003. \\
Hym98 & B. Hyman, \ul{The Fundamentals of Engineering Design},
Prentice-Hall, 1998. \\
IEEE Std 610.12-1990 & \ul{IEEE Standard Glossary of Software
Engineering Terminology}, IEEE Standard 610.12, 1990. \\
IEEE Std 830-1998 & \ul{IEEE Standard for Software Requirements
Specifications}, IEEE Standard 830, 1998. \\
IEEE Std 1233-1998 & \ul{IEEE Guide for Developing System Requirements
Specifications}, IEEE Standard 1233, 1998. \\
Jal97 & P. Jalote, \ul{An Integrated Approach to Software Engineering},
2\textsuperscript{nd} Edition, Spring-Verlag, New York, 1997. \\
Joh02 & D.W. Johnson and F. Johnson, \ul{Joining Together: Group Theory
and Group Skills}\emph{,} 8\textsuperscript{th} Edition, Prentice
Hall\emph{,} 2002\emph{.} \\
Kat93 & J.R. Katzenbach and D.K. Smith, \ul{The Wisdom of Teams:
Creating the High-Performance Organization}, HarperCollins, 1993. \\
Kei84 & D. Keirsey and M. Bates, \ul{Please Understand Me: Character and
Temperament Types}, Prometheus Nemesis, 1984. \\
Kel01 & T. Kelley and J. Littman, \ul{The Art of Innovation: Lessons in
Creativity from IDEO, America's Leading Design Firm,} Doubleday,
2001. \\
Leo95 & ``The World-Class Engineer,'' Penn State University Leonhard
Center, 1995. \\
Loc97 & ``The Ethics Challenge Leaders Guide,'' Lockheed Martin
Corporation, 1997. \\
Mci02 & ``The Ten C's for Evaluating Internet Resources,'' University of
Wisconsin-Eau Claire McIntyre Library,
\url{http://www.uwec.edu/library/Guides/tencs.html} , June, 2002. \\
Mcl93 & G.F. McClean, ``Integrating Ethics and Design,'' \emph{IEEE
Technology and Society Magazine}, vol. 12, no. 3, pp. 19--30, 1993. \\
Mic91 & M. Michalko, \ul{Thinkertoys}, Ten Speed Press, 1991. \\
MIL-HDBK 217F & \ul{Military Handbook for Reliability Prediction of
Equipment}, United States Department of Defense, 1991. \\
MIL-HDBK 881 & \ul{Department of Defense Handbook: Work Breakdown
Structure}, United States Department of Defense, 1998. \\
Nov00 & G. Novacek, ``Designing for Reliability, Maintainability, and
Safety: Part 1 Getting Started,'' \emph{Circuit Cellar}, Issue 125,
December, 2000. \\
Nov01 & G. Novacek, ``Designing for Reliability, Maintainability, and
Safety: Part 2: Digging Deeper,'' \emph{Circuit Cellar}, Issue 126,
January, 2001. \\
Osb48 & A.F. Osborn, \ul{Your Creative Power: How to Use Your
Imagination}, Scribner, 1948. \\
Osb63 & A.F. Osborn, \ul{Applied Imagination: Principles and Procedures
of Creative Problem-Solving}, Scribner, 1963. \\
Oul04 & \ul{The Glossary of Software Vulnerability Testing,} The
University of Oulu, Department of Electrical and Information Engineering
webpage, \url{http://www.ee.oulu.fi/research/ouspg/sage/glossary},
2004. \\
Pag88 & M. Page-Jones, \ul{The Practical Guide to Structured Systems
Design}, 2\textsuperscript{nd} Edition, Yourdan Press Computing Series,
1988. \\
Pet97 & T. Peters, \ul{The Circle of Innovation: You Can't Shrink Your
Way to Greatness}, Knopf, 1997. \\
Pet00 & J.F. Peters and W. Pedrycz, \ul{Software Engineering: An
Engineering Approach}, John Wiley and Sons, 2000. \\
Pri90 & S. Pritchard, ``Friends, Romans, Cost Engineers, \ldots{} Can We
Talk,'' \emph{Cost Engineering}, February, 1990. \\
Pug90 & S. Pugh, \ul{Total Design: Integrated Methods for Successful
Product Engineering}, Addison-Wesley, 1990. \\
Ros93 & R. Rosenburg, ``The Engineering Presentation--Some Ideas on How
to Approach and Present It,'' \emph{IEEE Transactions on Professional
Communication,} vol. PC-26, no. 1, pp. 191--193, December, 1993. \\
Roy70 & W.W. Royce, ``Managing the Development of Large Software
Systems: Concepts and Techniques,'' \emph{Proceedings of the IEEE
WESTCON}, 1970. \\
Rum98 & J. Rumbaugh, I. Jacobson, and G. Booch, \ul{Unified Modeling
Language Reference Manual}, Addison-Wesley, 1998. \\
Run99 & D.L. Runnels, ``How to Write Better Test Cases,'' International
Conference on Software Testing and Review, 12 pages, 1999. \\
Sat88 & T. Satay, \ul{Decision Making for Leaders: The Analytical
Hierarchy Process for Decisions in a Complex World}, University of
Pittsburgh, 1988. \\
Sat02 & J.W. Satzinger, \ul{Systems Analysis and Design in a Changing
World}, Course Technology, 2002. \\
Sch98 & K. Schrock, ``The ABCs of Website Evaluation,'' \emph{Classroom
Connect}, pp. 4--6, December 1998/January, 1999. Available at
\url{http://kathyschrock.net/abceval/}. \\
Sed04 & A. Sedra and K.C. Smith, \ul{Microelectronic Circuits}, Oxford
University Press, 2004. \\
Sha94 & J. Shapiro, ``Profession/Profile of George Heilmeier,''
\emph{IEEE Spectrum}, pp. 56--58, June, 1994. \\
Slo91 & P. Sloane , \ul{Lateral Thinking Puzzlers}, Sterling, 1991. \\
Slo93 & P. Sloane and D. MacHale, \ul{Challenging Lateral Thinking
Puzzles}, Sterling, 1993. \\
Slo94 & P. Sloane, \ul{Great Lateral Thinking Puzzles}, Sterling,
1994. \\
Smi04 & K.A. Smith, \ul{Teamwork and Project Management},
2\textsuperscript{nd} Edition, McGraw-Hill, 2004. \\
Som01 & I. Sommerville, \ul{Software Engineering}, 6\textsuperscript{th}
Edition, Addison Wesley, 2001. \\
Sta01 & J. Stadtmiller, \ul{Electronics: Project Management and Design},
Prentice Hall, 2001. \\
Ste89 & M.A. Stettner, ``How to Speak so Facts Come Alive,''
\emph{Chemical Engineering}, pp. 195, September, 1989. \\
Ste99 & W.P. Stevens, G.J. Myers, and L.L. Constantine, ``Structured
Design,'' \emph{IBM Systems Journal}, vol. 13, no. 2, pp. 231--256, 1999
(Reprinted from 1974). \\
Str02 & C.E. Stroud, \ul{A Designer's Guide to built-In Self Test},
Kluwer Academic Publishers, 2002. \\
Tel96 & Telcordia SR332, \ul{Reliability Prediction Procedure for
Electronic Equipment}, 1996. \\
Tuc65 & B. Tuckman, ``Developmental Sequence in Small Groups,''
\emph{Psychological Bulletin}, vol. 63, pp. 384--399, 1965. \\
Tuf03 & E. Tufte, ``PowerPoint is Evil: Power Corrupts, PowerPoint
Corrupts Absolutely\emph{,}'' \emph{Wired Magazine}, September, 2003.
Available at

\url{http://www.wired.com/wired/archive/11.09/ppt2.html}. \\
Ulr03 & K.T. Ulrich and S.D. Eppinger, \ul{Product Design and
Development}, 3\textsuperscript{rd} Edition, McGraw-Hill, 2003. \\
Van01 & A. Van Gorp and I. Van De Poel, ``Ethical Considerations in the
Engineering Design Process,'' \emph{IEEE Technology and Society
Magazine}, vol. 20, no. 3, pp. 15--22, 2001. \\
Vol03 & \emph{Volere Requirements Specification Template}, Version 9,
2003. \\
Wak00 & J. Wakerly, \ul{Digital Design: Principles and Practice},
3\textsuperscript{rd} Edition, Prentice Hall, 2000. \\
Wil95 & D. Wilemon, ``Cross-Functional Teamwork in Technology Based
Organizations,'' \emph{IEEE Engineering Management Conference}, pp.
74--79, 1995. \\
Wol01 & W. Wolf, \ul{Computers and Components: Principles of Embedded
Computing System Design}, Morgan Kaufmann, 2001. \\
Wol02 & W. Wolf, \ul{Modern VLSI Design}, Prentice Hall, 2002. \\
Yal01 & S. Yalamanchili, \ul{Introductory VHDL: From Simulation to
Synthesis}, Prentice Hall, 2001. \\
You89 & E. Yourdan, \ul{Modern Structured Analysis}, Yourdan Press
Computing Series, Prentice Hall, 1989. \\
\end{longtable}

\textbf{Concept Generation}
