\section{Problems}
\label{section:problems}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Explain the differences between black box and white box testing.
\item
  Identify a circuit simulator (analog or digital) that you are familiar
  with. Explain the features of this simulator, which increase the
  observability and controllability of the circuit being simulated.
\item
  A mobile robot is being built. It uses a two DC motors in a
  differential drive configuration, a microcontroller to control
  movement and an ultrasonic sensor to detect obstacles. The robot is
  built to wander around without bumping into objects. Explain how stubs
  could be used in testing to take the place of incomplete subsystems.
  Be specific.
\item
  Consider that you have an op amp integrated circuit package, such as
  the LM741 in Appendix C. What type of testing would be appropriate for
  testing this device? Write a short test plan for doing so.
\item
  Explain under what situations a matrix test is appropriate.
\item
  Explain under what situations a step-by-step is test appropriate.
\item
  Consider the stages of unit testing, integration testing, and
  acceptance testing. For each of these stages, identify the
  corresponding requirements that each test should be traceable to.
\item
  Consider the case study robot design in Section 7.3, which presents an
  acceptance test for the first system requirement. Develop an
  acceptance test for the second system requirement.
\item
  Consider the case study robot design in Section 7.3. Develop an
  integration test that demonstrates the combined operation of the DC
  motors, MCU, and range finder.
\item
  Consider the case study robot design in Section 7.3. Develop an
  integration test that demonstrates the combined operation of the
  digital compass, MCU, and LCD.
\item
  Consider the case study robot design in Section 7.3. Develop unit
  tests for range finder, the DC motors, the H-bridges, and the LCD.
\item
  \textbf{Project Application.} Develop an acceptance test suite for
  your project. The acceptance tests should apply to the engineering
  requirements developed for the system.
\item
  \textbf{Project Application.} Develop an integration test suite for
  your project. The integration tests should apply to the higher levels
  of the design architecture and address the interaction between
  functional units.
\item
  \textbf{Project Application.} Develop a unit test quite for your
  project. The unit tests should apply to the lowest level units in the
  design.
\end{enumerate}
