\section{Problems}
\label{problems}

\begin{enumerate}
\itemsep0em 
\def\labelenumi{\arabic{enumi}.}
\item
  In your own words, describe the difference between prescriptive and
  descriptive design processes. Cite examples of each.
\item
  Describe the relationship between the Problem Identification,
  Research, and Requirements Specification phases of the design process.
\item
  Describe the relationship between the Concept Generation and Design
  phases of the design process.
\item
  Construct a prescriptive design process for the Problem
  Identification, Research, Specification, Concept, and Design phases of
  the design process. The result should be a flow chart that contains
  decision blocks and iteration as necessary.
\item
  Describe the main differences between the VLSI and embedded system
  design processes.
\item
  Using the library or Internet, conduct research on the spiral software
  design process.

\begin{enumerate}
\itemsep0em 
\def\labelenumi{\alph{enumi})}
\item
  Outline the significant elements of the spiral software design
  process.
\item
  Describe the advantages and disadvantages of this relative to the
  waterfall model?
\end{enumerate}

\begin{quote}
Cite all reference used.
\end{quote}

\item
  Using the library or Internet, conduct research on the Extreme
  Programming design process.

\begin{enumerate}
\itemsep0em 
\def\labelenumi{\alph{enumi})}
\item
  Outline the significant elements of the Extreme Programming paradigm.
\item
  What are the pro and con arguments for this software development
  model?
\end{enumerate}

\begin{quote}
Be sure to cite references.
\end{quote}

\item
  \textbf{Project Application.} In preparation for project and team
  selection, develop a personal inventory that includes a list of five
  favorite technologies or engineering subjects that you are interested
  in pursuing. Also, list the strengths and weaknesses that you bring to
  a project team.
\end{enumerate}
