\section{Problems}
\label{section:problems}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Briefly describe the four properties of an engineering requirement.
\item
  Identify the three levels of standards usage and what is meant by each
  one.
\item
  For each of the engineering requirements below, determine if it meets
  the properties of abstractness, unambiguous, verifiable, and
  realistic. If a requirement does not satisfy the properties, restate
  it so that it does:


\begin{enumerate}
\def\labelenumi{\alph{enumi})}
\item
  The TV remote control will be easy to use.
\item
  The robot will identify objects in its path using ultrasonic sensors.
\item
  The car audio amplifier will be encased in aluminum and will operate
  in the automobile environment.
\item
  The audio amplifier will have a total harmonic distortion that is less
  than 2\%.
\item
  The robot will be able to move at speed of 1 foot/sec in any
  direction.
\item
  The system will employ smart power monitoring technology to achieve
  ultra-low power consumption.
\item
  The system shall be easy to use by a 12 year old.
\item
  The robot must remain operational for 50 years.
\end{enumerate}

  \item
    Provide three example engineering requirements that are technically
    verifiable, but not realistic.
  \item
    Describe the difference between \emph{verification} and
    \emph{validation}.
  \item
    Explain how \emph{validation} is performed for a Requirements
    Specification.
  \item
    Provide an example of a project (real or fictitious) where
    verification is successful, but validation is unsuccessful.
  \item
  \label{list:identifyMarkEngr}
    Consider the design of a common device such as an audio CD player,
    an electric toothbrush, or a laptop computer (or another device that
    you select). Identify potential marketing and engineering
    requirements. Consider those categories presented in 
    Section~\ref{section:engineering-requirements}, as
    well as any others that are applicable to the problem. You do not
    need to select the target values, but should identify the measures
    and units. Present the requirements in a table format as in 
    Table~\ref{table:audioRequireSpec}.
  \item
    Develop a marketing-engineering tradeoff matrix for the device
    selected in Problem~\ref{list:identifyMarkEngr}.
  \item
    Develop an engineering tradeoff matrix for the device selected in
    Problem~\ref{list:identifyMarkEngr}.
  \item
    Develop a list of potential standards that would apply to one of the
    devices proposed in Problem~\ref{list:identifyMarkEngr}, and for each indicate how it would
    apply to the design.
  \item
    \textbf{Project Application.} Develop a complete requirements
    document for your project as outlined in 
    Section~\ref{section:project-application-the-requirements-specification}. Make sure that
    the engineering requirements meet the five properties identified in
    the chapter. The team should complete the self-assessment checklist
    in Table~\ref{table:requirementsCheckList}.
\end{enumerate}