% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\emph{\textbf{Chapter 11 -- Ethics in Design and the Profession}}

\textbf{1.Describe the relationship between ethics and morals. {[}R{]}}

\begin{quote}
Ethics and morals are two terms that are often used interchangeably.
Ethics is the philosophy or study of moral obligations and the choices
to be made by individuals. The choices made are based upon personal
beliefs, and the decisions have relational repercussions. On the other
hand, morals are fundamental principles, laws, or rules that are
generally accepted and practiced by religions and belief systems of the
world.
\end{quote}

\textbf{2.Describe the differences between morals and values. {[}R{]}}

\begin{quote}
Morals are universal principles that govern behavior and are embodied in
all major religions and belief systems of the world. Morals are laws or
rules that are upheld by the masses as being good. However, a value is
something that a certain body of people find worthwhile. A value is not
often universally accepted because it's global relevance or because it
may be good or bad.
\end{quote}

\textbf{3.Which patent is most relevant for engineering inventions, a
design patent or utility} \textbf{patent? Why?{[}R{]}}

\begin{quote}
The utility patent is most relevant for engineering inventions, because
a design patent focuses more on the aesthetic design issues and less on
the manner of technology being used.
\end{quote}

\textbf{4.What are the criteria that are used in evaluating patents?
{[}R{]}}

\begin{quote}
A patent must be novel, non-obvious, and useful. In order to be novel,
the patent must be an original and new idea. Non-obvious states that
another person would not be expected to develop the same idea based upon
existing technology. Usefulness describes the fact that the device must
perform a useful function that is able to be reduced to practice.
\end{quote}

\textbf{5.Explain the importance of claims in a patent application.
{[}R{]}}

\begin{quote}
Claims are the legal description of the invention and its unique
aspects. They are used to determine if another party is infringing upon
a patent; hence, they must be carefully thought out and properly worded.
Because claims provided a patents protection, a very broad or very
specific claim may be disadvantageous.
\end{quote}

\textbf{6.Discuss the tradeoffs involved between using patents and trade
secrets to protect} \textbf{intellectual property. {[}R{]}}

\begin{quote}
Unlike patents, trade secrets are not released to the general public.
Ideas are kept secret among a select number of people, who are held
liable via non-disclosure agreements. Protecting intellectual property
by means of trade secrets assists in keeping other companies from
finding out about it; however, once the secret is revealed, it is fair
game for competitors to reverse-engineer the technology.
\end{quote}

\textbf{7.When can reverse-engineering be used, and how can the
information obtained from it} \textbf{be used? {[}R{]}}

\begin{quote}
Reverse-engineering is legal as long as the method of obtaining the
information was legal. The information obtained from the
reverse-engineering may not be copied it unless legally allowed to do
so. Breaking encryptions is an example of illegally obtaining
information.
\end{quote}

1

\textbf{8.What is the difference between negligence and strict liability
in tort law? {[}R{]}}

\begin{quote}
Negligence focuses on the method of producing a product and its effects
on the end-user. It must be shown that the manufacturer did not follow
reasonable standards and rules that apply to the situation and also
committed a wrongful act. Negligence has three different levels --
simple, gross, and criminal. These claims may be brought for design
flaws, manufacturing defects, and failing to warn the user of safety
hazards.

Strict liability is a less stringent standard than negligence and it
focuses product itself and its effect on the end-user. Regardless of the
standards used, or not used, in manufacturing, if the product had a
defect or was dangerous when it left the hands of the manufacturer, the
manufacturer may be held liable.
\end{quote}

\textbf{9.For the case study presented below, apply the ethical decision
making paradigm presented in Section 11.5 to analyze the situation.
Present potential solutions to the scenario and provide a discussion of
them.{[}A{]}}

\begin{quote}
This case-study is one that we use nearly ever year for an in-class
discussion. It always provokes the most debate among our students, and
they split almost evenly on the sides of the two companies. Let's go
through the steps of the process:

\uline{Step 1: Gather Information}

Here are some questions to consider:

•Is Company P doing anything illegal? How about unethical? It certainly
does appear that this is unethical in what Company P is trying to do --
they are trying to represent themselves as Company C. It is not clear if
this is illegal -- probably not.

•However, many students have argued strongly that Company C may be
trying to develop a monopoly. Is it monopolistic? It does not mean other
companies cannot supply disks, only that they cannot use these
diagnostics. In fact, other companies could probably also develop
software to carry out similar diagnostics.

•Company C could have done a better job of protecting itself by using
encryption or some other method to protect its diagnostics.

\uline{Step 2: Identify the Stakeholders}

The following people will be affected by the decision.

•Company C. Company C will be hurt monetarily by this action.

•Company P. They stand to gain in market shares. They could be hurt if
legal action is brought against them. This could also hurt their
reputation.

•Users of the disks of Company P. Company C could change part of the
protocols for the diagnostics, rendering the diagnostics on Company P
disks useless.

\uline{Step 3: Identify Relevant Ethical Values}

•IEEE Code Element 3. This is not a an honest claim by Company P.

•IEEE Code Element 9. This could hurt company C.
\end{quote}

2

\begin{quote}
•IEEE Code Element 9. The management of Company P is clearly asking
their employee to do something unethical.

\uline{Step 4: Determine a Course of Action}

Some possible courses of action are:

A)You, the engineer, could follow the advice of management.

B)You, the engineer, could recommend writing your own software
diagnostic code and have the users of your disks install and utilize
that.

C)You could negotiate a deal with Company C to use their diagnostics and
pay them a royalty based upon the number of disk drives sold.

D)You could simply refuse to do it and explain to the management why
not.

Options B, C, and D are the most ethical and advisable. Following what
the management recommends is unethical. B and C seem like good
approaches to provide the service in an ethical way.
\end{quote}

\textbf{10.For the case study presented below, apply the ethical
decision making paradigm presented in Section 11.5 to analyze the
situation. Present potential solutions to the scenario and provide a
discussion of them.{[}A{]}}

\begin{quote}
\uline{Step 1: Gather Information}

This is a case where some unintended actions lead to an ethical dilemma.
In its original use, the software was not necessarily to be distributed
overseas, at least the engineer did not know that it would be. The
supervisor's response is not very good, even if he is correct in that it
the software would not be used outside of the company, which it turns
out it was.

\uline{Step 2: Identify Stakeholders}

•The employees of the company -- this could bring legal action against
the company.

•US citizens. The reason that the government passed this law was so that
the encryption algorithms would not fall into hands of people outside of
the US who would want to harm its cirtizens.

\uline{Step 3: Relevant Ethical Values} (from the IEEE Code)

•\#1. This could endanger the welfare of the public.

•\#7. Acknowledge and correct errors. Although this was perhaps an
unintentional error, it should be acknowledged and corrected.

•\#10. Again, the supervisor gave bad advice here that did not assist
others in being ethical.

\uline{Step 4: Determine a Course of Action}

A)Do nothing.
\end{quote}

3

\begin{quote}
B)Bring this to the attention of your supervisor. If not, go to the next
level supervisor, etc, until the issue is resolved.

C)Be a whistleblower and bring it to the attention of the government.

A is clearly not a good option, and something should be done to resolve
this issue. Option B makes the most sense in that attempts should be
made to resolve the issue internally. Option C makes sense only after
option B is exhausted. Failure to resolve it internally would lead one
to believe that this could bring harm to the public.
\end{quote}

\textbf{11.For the case study presented below, apply the ethical
decision making paradigm presented in Section 11.5 to analyze the
situation. Present potential solutions to the scenario and provide a
discussion of them.{[}A{]}}

\begin{quote}
\uline{Step 1: Gather Information}

The measurement equipment in question has a design fault according to
your analysis of the problem. It is not clear from the problem statement
whether or not a failure of this equipment could endanger the health of
a patient, but presumably it could.

\uline{Step 2: Relevant Ethical Values from the Code}

•\#1. Could potentially endanger the safety of a patient.

•\#3. To be honest in stating claims. In this case the manager is not
being honest in stating that there is no problem with the equipment.

•\#7. To accept criticism and correct errors that may exist.

•\#8. To avoid injuring others.

\uline{Step 3: Stakeholders}

Both companies, all patients who are monitored by the system, and the
hospitals who use the equipment.

\uline{Step 4: Determine a Course of Action}

In this case, the engineer should do something. The potential of the
design fault harming somebody is a real risk. You could present a design
fix to the management of your company. You should also bring this to
their attention until the issue is resolved. Depending upon the severity
of the potential problem of inaction, it may be necessary to blow the
whistle and go outside of the company.
\end{quote}

\textbf{12.For the case study presented below, apply the ethical
decision making paradigm presented in Section 11.5 to analyze the
situation. Present potential solutions to the scenario and provide a
discussion of them.{[}A{]}}

\begin{quote}
\uline{Step 1: Gather Information}

Jerry is probably being nice in this case to supervise the installation
and not interfere with your vacation. However, the reality is that it is
your responsibility to supervise the installation.

\uline{Step 2: Identify Stakeholders}
\end{quote}

4

\begin{quote}
You, your company, the other company (Boulding), and the people who
utilize the equipment.

\uline{Step 3: Relevant Ethical Values}

•\#1. Need to make a decision that is consistent with the health \&
safety of the users.

•\#2. To avoid conflicts of interest. The engineer has a conflict mainly
because of the issue of the vacation. Otherwise, it is likely that the
engineer (you) would stay to finish the job without question.

•\#4. To reject bribery. It is not clear that there is bribery in this
case, but it is possible that Jerry would ask for a return favor in the
future.

\uline{Step 4: Determine a Course of Action}

A)Turn down the offer and stay to oversee the installation.

B)Call your company and explain the situation. See what they recommend.

C)Go skiing -- Jerry can handle it!

Option A is the safest course of action. However, Option B is a pretty
good idea. It may turn out that your company would offer to send another
engineer, or perhaps agree that Jerry is capable of completing the
installation. Option C) sounds like fun, but could lead to problems,
particularly if anyone is ever injured by the equipment.
\end{quote}

5

\end{document}
